Deep mutational scanning of hemagglutinin helps distinguish the evolutionary fate of human H3N2 influenza virus lineages

### 2018-01-15 paper/manuscript.tex
Add a few bullet points to Discussion
Add a bit more to Methods

\begin{itemize}
\item{Antigenic characteristics play a large role in determining strain success. We therefore need to know how mutations affect antigenicity.}
\item{non-HA segments are important too}
\end{itemize}

@@

\subsection*{Inference of phylogenetic trees}
\comment{John to add methods here. We downloaded X sequences from the Influenza Virus Resource ?.... etc. inferred the tree, ancestral state reconstruction, visualized the tree...}
To parse out trunk mutations from side branch mutations, we first defined a set of recent nodes sampled on or after Jan. 1, 2017, and traced these nodes back to their most recent common ancestor.

@@

@@

\acknow{We thank Sarah Hilton, Hugh Haddox, Sidney Bell...the Fred Hutch Genomics Core...
Funding...}

>>>>

\begin{itemize}
\item{These experimental measurements have utility in revealing differences between successful and unsuccessful lineages over 50 y of human influenza virus evolution.}
\item{We have only measured the effect of mutations to HA on viral growth, but there are certainly other determinants of strain success}
\item{Antigenic characteristics play a large role in determining strain success. We therefore need to know how mutations affect antigenicity.}
\item{non-HA segments are important too}
\end{itemize}

@@

\subsection*{Inference of phylogenetic trees}
\comment{John to add methods here. We downloaded X sequences from the Influenza Virus Resource ?.... etc. subsampled how? inferred the tree, ancestral state reconstruction, visualized the tree...}
To parse out trunk mutations from side branch mutations, we first defined a set of recent nodes sampled on or after Jan. 1, 2017, and traced these nodes back to their most recent common ancestor. 
We defined all branches ancestral to this most recent common ancestor of recently sampled nodes as the trunk.
All nodes descended from the trunk were defined as side branch nodes.
Nodes descended from the most recent common ancestor were defined as unresolved.

@@

\subsection*{Analysis of mutational shifts}

@@

\acknow{We thank Sarah Hilton, Hugh Haddox, Sidney Bell for helpful discussions about data analysis...the Fred Hutch Genomics Core...
Funding...}
